\jaxcosmo: An End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2023-01-11 paper_OJA.tex
Add author contribution dlanzieri

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

\affiliation{$^1$Université Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration \textbf{J. Zuntz:} Investigation, Writing.

>>>>

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,\\
D. Lanzieri$^4$\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

\affiliation{$^1$Université Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France \\
 $^4$Université Paris Cité, Université Paris-Saclay, CEA, CNRS, AIM, F-91191, Gif-sur-Yvette, France}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration \textbf{J. Zuntz:} Investigation, Writing.
\textbf{D. Lanzieri:}, Software and validation for redshift distribution.
